---
title: "Whole microbiome network analysis"
author: "Bea"
date: "2023-03-27"
output: html_document
---

```{r setup, include=FALSE}
library("phyloseq")
library("ggplot2")
library("RColorBrewer")
library("patchwork")
library("microbiome")
library("ape")
library("vegan")
#library("decontam")
library('tidyverse')
library("ecodist")
library("viridis")
library("igraph")
library("GGally")
library("intergraph")
library("network")
library("SpiecEasi")
library("ggpubr")

knitr::opts_chunk$set(echo = TRUE)
```

## CURATING THE DATASETS

After calculating the differentially abundant microorganisms present in both the whole microbiome. We need to investigate first where each microorganisms is more abundant: Ouseburn or Nafferton

```{r microbiome}
# Create a jittered boxplot for each genus, it will be curated later

abudant_taxa_list <- row.names(diff_ab_taxa)
ab_pseq <- prune_taxa(abudant_taxa_list, scr_pseq)
ab_pseq <- microbiome::transform(ab_pseq, transform = "compositional")
ab_pseq_order <- ab_pseq %>% 
  tax_glom("Genus")
phyloseq::taxa_names(ab_pseq_order) <- phyloseq::tax_table(ab_pseq_order)[, "Genus"]
microbial_df <- phyloseq::psmelt(ab_pseq_order) 
microbial_df %>%
  ggplot(data = ., aes(x = Farm, y = Abundance)) +
    geom_boxplot() +
    geom_jitter(aes(color = OTU), height = 0, width = .2) +
    labs(x = "", y = "Abundance\n") +
    facet_wrap(~ OTU, scales = "free", ncol = 5) +
    theme(legend.position = "none") +
    scale_color_manual(values = col_vector74)
```
Now, we do the same for viruses

```{r virome}
vabudant_taxa_list <- row.names(vdiff_ab_taxa)
vab_pseq <- prune_taxa(vabudant_taxa_list, scr_vseq)
vab_pseq <- microbiome::transform(vab_pseq, transform = "compositional")
ab_vseq_genus <- vab_pseq %>% 
  tax_glom("Genus")
phyloseq::taxa_names(ab_vseq_genus) <- phyloseq::tax_table(ab_vseq_genus)[, "Genus"]

viral_df <- phyloseq::psmelt(ab_vseq_genus) 
viral_df %>% 
  ggplot(data = ., aes(x = Farm, y = Abundance)) +
    geom_boxplot(outlier.shape = NA) +
    geom_jitter(aes(color = OTU), height = 0, width = .2) +
    labs(x = "", y = "Abundance\n") +
    facet_wrap(~ OTU, scales = "free") +
    theme(legend.position = "none")
```

## NETWORK ANALYSIS OF MICROBIOME AND VIROME DATA

Now let's curate the network by only using the core microbiome to calculate the edges and nodes

```{r}
core.names = taxa_names(pseq.core)
vcore.names = taxa_names(vseq.core)
pseq.net = prune_taxa(core.names, scr_pseq)
vseq.net = prune_taxa(vcore.names, scr_vseq)
```

Now, let's subset to the top 25 most abundant OTU and vOTU to start the network analysis, as we'll use this to curate the final graph (the original will be too large)

```{r}
top25OTU.names = names(sort(taxa_sums(pseq.net), TRUE)[1:10])
top25OTU = prune_taxa(top25OTU.names, scr_pseq) 

top25vOTU.names = names(sort(taxa_sums(vseq.net), TRUE)[1:10])
top25vOTU = prune_taxa(top25vOTU.names, scr_vseq) 
```

Extract TOP25 OTU/vOTU from original count data first. We'll use this to curate the network in the final steps

```{r}
microbe_top25 <- prune_taxa(taxa_names(top25OTU), scr_pseq)
viral_top25 <- prune_taxa(taxa_names(top25vOTU), scr_vseq)
```


# Split datasets by farm

```{r}
naff_phy <- subset_samples(pseq.net, Farm == "Nafferton")
ous_phy <- subset_samples(pseq.net, Farm == "Ouseburn")

v_naff_phy <- subset_samples(vseq.net, Farm == "Nafferton")
v_ous_phy <- subset_samples(vseq.net, Farm == "Ouseburn")
```

We use absolute counts for SpiecEasi, as the program will automatically transform the data into compositional metrics and normalization.

```{r echo=FALSE}
#Reorder samples for analysis in spiec easi
order <- c(colnames(otu_table(naff_phy)))
otu_table(v_naff_phy) <- otu_table(v_naff_phy)[, order]
order2 <- c(colnames(otu_table(ous_phy)))
otu_table(v_ous_phy) <- otu_table(v_ous_phy)[, order2]
```

```{r echo=FALSE}
multi.kingdom.naff <- multi.spiec.easi(list(naff_phy, v_naff_phy), method="mb", lambda.min.ratio=1e-2, nlambda=20, pulsar.params=list(rep.num=100))
multi.kingdom.ous <- multi.spiec.easi(list(ous_phy, v_ous_phy), method="mb", lambda.min.ratio=1e-2, nlambda=20, pulsar.params=list(rep.num=100))
```
Let's start with the plots for each of the networks

```{r}
## Plot the network and colour the nodes by Phylum
spiec.graph.naff=adj2igraph(getRefit(multi.kingdom.naff), vertex.attr=list(name=c(taxa_names(naff_phy), taxa_names(v_naff_phy))))
spiec.graph.ous=adj2igraph(getRefit(multi.kingdom.ous), vertex.attr=list(name=c(taxa_names(ous_phy), taxa_names(v_ous_phy))))
```

## CREATE A SUBNETWORK WITH TOP OTUS AND VOTUs

For the construction of the main networks, we've used the core microbial and viral networks (hundreds of taxa), and we can now curate those networks to show only the top taxa we are interested in, we the advantage that we can also recover the nodes that connect to them, retaining important information.

```{r set_data}
#Set the data we are going to plot first
query = multi.kingdom.ous
mgraph = spiec.graph.ous
phy = ous_phy
vphy = v_ous_phy

#Try nafferton with bac+euk
#query = resultsbaek[1,1][[1]]
#mgraph = resultsbaek[2,1][[1]]
#phy = bc_naf
#vphy = fc_naf

```


```{r}
# make a list of the names of the nodes of interest from top otus
#rownames(tax_table(microbe_top25)) <- tax_table(microbe_top25)[,c('Genus', "Species")]
nodes_of_interest <- c(taxa_names(microbe_top25), taxa_names(viral_top25))
#nodes_of_interest <- c(taxa_names(top_bac_naf), taxa_names(top_euk_naf))

# select the nodes having these names
selnodes <- V(mgraph)[name %in% nodes_of_interest]
# get their network neighborhood 
selegoV <- ego(mgraph, order=1, nodes = selnodes, mode = "all", mindist = 0)

# turn the returned list of igraph.vs objects into a graph
qgraph <- induced_subgraph(mgraph,unlist(selegoV))
```

Obtain standard measures from the graph, including network degree and betweenness

```{r net_measures, results='hide'}
netw = single.graph.naff

# Degree centrality and average degree
degree.cent <- centr_degree(netw, mode = "all")
degree.cent$res

mean.degr <- mean(igraph::degree(netw, mode = "all"))
mean.norm.degr <- mean(igraph::degree(netw, mode = "all", normalized = T))

# Closeness
closeness.cent <- igraph::closeness(netw, mode="all")
closeness.cent

# Transitivity or clustering coefficient
#transitivity.cent <- transitivity(netw, type = "average")
transitivity.cent <- transitivity(netw, type = "global")
transitivity.cent

# Modularity
wtc <-  cluster_walktrap(netw)
modularity.cent <- modularity(netw, membership(wtc))
modularity.cent

# Average path length
pathlength.cent <- mean_distance(netw, directed = FALSE)
pathlength.cent

# Average normalized betweenness
between.ces <- igraph::betweenness(netw, directed = T, normalized = T)
mean.bet <- mean(between.ces)
```

```{r}
mean.degr
mean.norm.degr
transitivity.cent
modularity.cent
pathlength.cent
mean.bet
```


## PLOT THE NETWORK

```{r plot_set, results='hide'}
# Visualize using ggnet

# Col vector up to 74 color samples
col_vector74 = c("#7FC97F","#BEAED4","#FDC086","#FFFF99","#386CB0","#F0027F","#BF5B17","#666666","#1B9E77","#D95F02","#7570B3","#E7298A","#66A61E","#E6AB02","#A6761D","#666666","#A6CEE3","#1F78B4","#B2DF8A","#33A02C","#FB9A99","#E31A1C","#FDBF6F","#FF7F00","#CAB2D6","#6A3D9A","#FFFF99","#B15928","#FBB4AE","#B3CDE3","#CCEBC5","#DECBE4","#FED9A6","#FFFFCC","#E5D8BD","#FDDAEC","#F2F2F2","#B3E2CD","#FDCDAC","#CBD5E8","#F4CAE4","#E6F5C9","#FFF2AE","#F1E2CC","#CCCCCC","#E41A1C","#377EB8","#4DAF4A","#984EA3","#FF7F00","#FFFF33","#A65628","#F781BF","#999999","#66C2A5","#FC8D62","#8DA0CB","#E78AC3","#A6D854","#FFD92F","#E5C494","#B3B3B3","#8DD3C7","#FFFFB3","#BEBADA","#FB8072","#80B1D3","#FDB462","#B3DE69","#FCCDE5","#D9D9D9","#BC80BD","#CCEBC5","#FFED6F")

# Add edged colors based on nodes connected

#The inverse covariance matrix is obtained via a form of regression
betaMat=as.matrix(symBeta(getOptBeta(query)))

otu.ids <- colnames(query[[1]]$data)
edges=E(qgraph)
edge.colors=c()
edge.weight=c()
for(e.index in 1:length(edges)){
  adj.nodes=ends(qgraph,edges[e.index])
  xindex=which(otu.ids==adj.nodes[1])
  yindex=which(otu.ids==adj.nodes[2])
  beta=betaMat[xindex,yindex]
  if(beta>0){
    edge.colors=append(edge.colors,"forestgreen")
    #edge.weight= format(beta*100,digits=3)
    weight= format(beta*100,digits=3)
    edge.weight=append(edge.weight,weight)
    
    cat("Beta pos:",beta,"\n")
    
  }else if(beta<0){
    edge.colors=append(edge.colors,"red")
    weight= format(beta*100,digits=3)
    edge.weight=append(edge.weight,weight)
    
    cat("Beta neg:",beta,"\n")
    
    
  }
}

E(qgraph)$color=edge.colors
E(qgraph)$weight=edge.weight

#How many nodes connected at specific rank
nb_nodes <- vcount(qgraph)
tax_table(phy) <- tax_table(phy)[,"Genus"]
tax_table(vphy) <- tax_table(vphy)[,'Genus']

#Taxa names for microbes
otu_ids <- V(qgraph)$name
idx <- which(row.names(tax_table(phy)) %in% otu_ids)
taxa <- as.character(tax_table(phy)[,"Genus"])[idx]

#Taxa names for virus
votu_ids <- V(qgraph)$name
vidx <- which(row.names(tax_table(vphy)) %in% votu_ids)
vtaxa <- as.character(tax_table(vphy)[,"Genus"])[vidx]

ig2 <- asNetwork(qgraph)
network.vertex.names(ig2) <- c(taxa, vtaxa)

net <- ig2
net %v% "Genus" = as.character(c(taxa, vtaxa))
y= col_vector74[1:nb_nodes]
#y=viridis(n = 35, option = "viridis")
names(y) <- levels(as.factor(c(taxa, vtaxa)))
```

```{r plots}
#Plot the network

p_naff <-  ggnet2(net,
             color = "Genus",
             palette = y,
             alpha = 0.75,
             size = "degree", 
             #edge.label = NULL, 
             #edge.size=1,
             #edge.label = "none",
             edge.color="color",
             edge.alpha = 0.5,
             label = TRUE, 
             label.size = 3
             #edge.label.size = 2
             ) +
  guides(col="none", size ="none") +
  #geom_nodelabel_repel(label = network.vertex.names(net)) +
  ggtitle("Nafferton network")
  

p_ous <- ggnet2(net,
            color = "Genus",
            palette = y,
            alpha = 0.75,
            size = "degree", 
            #edge.label = "weight", 
            #edge.size=1,
            edge.color="color",
            edge.alpha = 0.5,
            label = TRUE, 
            label.size = 3
            #edge.label.size = 2
            ) +
  guides(col="none", size = "none") +
  #geom_text_repel() +
  ggtitle("Ouseburn network")


whole_plot <- ggarrange(p_naff, p_ous, ncol = 2, nrow = 1)
ggsave(file="whole_net_plot_top10.svg", plot=whole_plot, width=18, height=10)
```





