---
title: "Farm network by kingdom"
author: "Bea"
date: "2023-05-09"
output: html_document
---

```{r setup, include=FALSE}
library("phyloseq")
library("ggplot2")
library("RColorBrewer")
library("patchwork")
library("microbiome")
library("ape")
library("vegan")
#library("decontam")
library('tidyverse')
library("ecodist")
library("viridis")
library("igraph")
library("GGally")
library("sna")
library("intergraph")
library("network")
library("SpiecEasi")
library("ggpubr")
library("gridExtra")
library("grid")

knitr::opts_chunk$set(echo = TRUE)
```

## Divide core microbiome by kingdom

We are doing this to observe how the network changes the more layers you add to it. We have already created these objects with the raw counts in other Rmd files. Now it's time to calculate the core microbiomes in each of those objects. We also need to separate by farm.

```{r divide}
## Function for sub-sampling the phyloseq objects. Creates a list with the phyloseq objects for Naff and Ouseburn separately
net_ps <- function(phylo) {
  naf <- subset_samples(phylo, Farm == "Nafferton")
  ous <- subset_samples(phylo, Farm == "Ouseburn")
  #relnaf <- microbiome::transform(naf, "compositional")
  #relous <- microbiome::transform(ous, "compositional")
  #cornaf <- core(relnaf, detection = 1/100, prevalence = 25/100)
  #corous <- core(relous, detection = 1/100, prevalence = 25/100)
  namesnaf <-  names(sort(taxa_sums(naf), TRUE)[1:100])
  namesous <- names(sort(taxa_sums(ous), TRUE)[1:100])
  pnaf <-  prune_taxa(namesnaf, naf)
  pous <- prune_taxa(namesous, ous)
  plist <- list(pnaf, pous)
  return(plist)
}

# Function to store the desired phyloseq object from the list obtained from net_ps()
psob_fun <- function(phylolist, numb) {
  obj <- phylolist[[numb]]
  return(obj)
}
```

Obtain the corresponding core microbiome phyloseq objects by farm and kingdom.

```{r}
#Archaea
acore_list <- net_ps(a_pseq) #List of phyloseq objects
ac_naf <- psob_fun(acore_list, 1) #Phyloseq for Nafferton
ac_ous <- psob_fun(acore_list, 2) #Phyloseq for Ouseburn
#Bacteria
bcore_list <- net_ps(b_pseq)
bc_naf <- psob_fun(bcore_list, 1)
bc_ous <- psob_fun(bcore_list, 2)
#Eukaryotes
fcore_list <- net_ps(f_pseq)
fc_naf <- psob_fun(fcore_list, 1)
fc_ous <- psob_fun(fcore_list, 2)
#Viruses
# For viruses we need to reorder
sam_order <- sample_names(b_pseq)
otu_table(scr_vseq) <- otu_table(scr_vseq)[,sam_order]
vcore_list <- net_ps(scr_vseq)
vc_naf <- psob_fun(vcore_list, 1)
vc_ous <- psob_fun(vcore_list, 2)
```

Now let's create the functions that will allow us to calculate the networks and the graphs

```{r}
# Function to calculate the network correlations and the graph using both SPIEC-EASI and igraph
net_fun <- function(phylo) {
  net <- spiec.easi(phylo, method="mb", lambda.min.ratio=1e-2, nlambda=20, pulsar.params=list(rep.num=100))
  pl.net <- adj2igraph(getRefit(net), vertex.attr=list(name=taxa_names(phylo)))
  plist <- list(net, pl.net)
  return(plist)
}
```

```{r}
# We can apply the network function directly to the list of phyloseq objects, and it will return a list of results back

results <- lapply(acore_list, net_fun) #It will return a list of the results
resultsb <- lapply(bcore_list, net_fun)
resultsf <- lapply(fcore_list, net_fun)
resultsv <- lapply(vcore_list, net_fun)
```
Create a function to store all metrics associated with the networks

```{r}
# Function to extract the only graphs from each farm. Returns a list that can be fed to the next function
grap_list <- function(netlist){
  result <-  list()
  for (x in 1:length(netlist)) {
    graph <- netlist[[x]][[2]]
    result[x] <- list(graph)
  }
  return(result)
}

# Function to calculate all the graph metrics
net_met <- function(graph) {
  # Degree centrality and average degree
  degree <- centr_degree(graph, mode = "all")
  # Mean degree
  d.mean <- mean(igraph::degree(graph, mode = "all"))
  d.mean.norm <- mean(igraph::degree(graph, mode = "all", normalized = T))
  # Closeness
  closen <- igraph::closeness(graph, mode="all")
  # Transitivity
  trans <- transitivity(graph, type = "average")
  # Modularity
  wtc <- cluster_walktrap(graph)
  modular <- modularity(graph, membership(wtc))
  # Average path length
  pathlen <- mean_distance(graph, directed = FALSE)
  # Av. normalized betweenness 
  between <- igraph::betweenness(graph, directed = T, normalized = T)
  mean.bet <- mean(between)
  met_list <- list(degree, d.mean, d.mean.norm, closen, trans, modular, pathlen, mean.bet)
  return(met_list)
}
```

Apply the metrics for each set of graphs. Resulst are stored in lists too.

```{r}
# For archaea

a_graphs <- grap_list(results) # List of graphs for each farm with only the Archaea
arch_metrics <- lapply(a_graphs, net_met) # List of metrics for each graph

# For bacteria
b_graphs <- grap_list(resultsb)
bac_metrics <- lapply(b_graphs, net_met)

# For eukaryotes
f_graphs <- grap_list(resultsf)
fun_metrics <- lapply(f_graphs, net_met)

# For viruses
v_graphs <- grap_list(resultsv)
vir_metrics <- lapply(v_graphs, net_met)

```

## Newtork plot functions

```{r color_edges}

# Visualize using ggnet

# Col vector up to 74 color samples
col_vector74 = c("#7FC97F","#BEAED4","#FDC086","#FFFF99","#386CB0","#F0027F","#BF5B17","#666666","#1B9E77","#D95F02","#7570B3","#E7298A","#66A61E","#E6AB02","#A6761D","#666666","#A6CEE3","#1F78B4","#B2DF8A","#33A02C","#FB9A99","#E31A1C","#FDBF6F","#FF7F00","#CAB2D6","#6A3D9A","#FFFF99","#B15928","#FBB4AE","#B3CDE3","#CCEBC5","#DECBE4","#FED9A6","#FFFFCC","#E5D8BD","#FDDAEC","#F2F2F2","#B3E2CD","#FDCDAC","#CBD5E8","#F4CAE4","#E6F5C9","#FFF2AE","#F1E2CC","#CCCCCC","#E41A1C","#377EB8","#4DAF4A","#984EA3","#FF7F00","#FFFF33","#A65628","#F781BF","#999999","#66C2A5","#FC8D62","#8DA0CB","#E78AC3","#A6D854","#FFD92F","#E5C494","#B3B3B3","#8DD3C7","#FFFFB3","#BEBADA","#FB8072","#80B1D3","#FDB462","#B3DE69","#FCCDE5","#D9D9D9","#BC80BD","#CCEBC5","#FFED6F")

# Add edged colors based on nodes connected

## Create fucntion to color the edges of the graph based on its positive or negative correlation. 
#The inverse covariance matrix is obtained via a form of regression, this way we calculate the direction (pos or neg) of the edges
#Returns a list with the covariance matrix, the ids to be sued for the labeling, and the colors and weights of the edges.

color_edges <- function(spiec, qgraph){
  betaMat=as.matrix(symBeta(getOptBeta(spiec)))
  otu.ids <- colnames(spiec[[1]]$data)
  edges=E(qgraph)
  edge.colors=c()
  edge.weight=c()
  for(e.index in 1:length(edges)){
    adj.nodes=ends(qgraph,edges[e.index])
    xindex=which(otu.ids==adj.nodes[1])
    yindex=which(otu.ids==adj.nodes[2])
    beta=betaMat[xindex,yindex]
    if(beta>0){
      edge.colors=append(edge.colors,"forestgreen")
      #edge.weight= format(beta*100,digits=3)
      weight= format(beta*100,digits=3)
      edge.weight=append(edge.weight,weight)
      cat("Beta pos:",beta,"\n")
    }
    else if(beta<0){
      edge.colors=append(edge.colors,"red")
      weight= format(beta*100,digits=3)
      edge.weight=append(edge.weight,weight)
      cat("Beta neg:",beta,"\n")
    }
  }
  return(list(betaMat, otu.ids, edge.colors, edge.weight))
}

```

```{r get_color_edges}
# Try functions with the result list from SPIEC-EASI and igraph
# We need to split by farm the original list with the graph and spiec results, as they contain both farms

#Archea
a_naff <- results[[1]]
a_ous <- results[[2]]
arch_colors_naff <- do.call(color_edges, a_naff)
arch_colors_ous <- do.call(color_edges, a_ous)

#Bacteria
b_naff <- resultsb[[1]]
b_ous <- resultsb[[2]]
bact_colors_naff <- do.call(color_edges, b_naff)
bact_colors_ous <- do.call(color_edges, b_ous)

#Eukaryotes
f_naff <- resultsf[[1]]
f_ous <- resultsf[[2]]
euk_colors_naff <- do.call(color_edges, f_naff)
euk_colors_ous <- do.call(color_edges, f_ous)

#Viruses
v_naff <- resultsv[[1]]
v_ous <- resultsv[[2]]
vir_colors_naff <- do.call(color_edges, v_naff)
vir_colors_ous <- do.call(color_edges, v_ous)
```

After calculating the value of each edge, and assigning a color to the positive and negative interaction, we need to create a function to produce the plots: one for each farm and kingdom (a total of 6 initially).

```{r get_net}
## Function to produce network plot

get_net <- function(qgraph, physeq, colres){
  # Associate colors to graph
  E(qgraph)$color=colres[[3]]
  E(qgraph)$weight=colres[[4]]
  # Pick node name to the Genus level
  tax_table(physeq) <- tax_table(physeq)[,"Phylum"]
  #Taxa names for microbes
  otu_ids <- V(qgraph)$name
  idx <- which(row.names(tax_table(physeq)) %in% otu_ids)
  taxa <- as.character(tax_table(physeq)[,"Phylum"])[idx]
  net <- asNetwork(qgraph)
  network.vertex.names(net) <- taxa
  net %v% "Phylum" = as.character(taxa)
  return(list(net, taxa))
}

nb_nodes <- c(vcount(b_ous_topnet) + vcount(b_naff_topnet))
y = colorRampPalette(col_vector74)(nb_nodes)
names(y) <- levels(as.factor(c(b_net_ous[[2]], b_net_naff[[2]])))
get_netplot <- function(qgraph, net, taxa, colpalette){
  #nb_nodes <- vcount(qgraph)
  #y= colorRampPalette(col_vector74)(nb_nodes)
  #names(y) <- levels(as.factor(taxa))
  netplot <- ggnet2(net,
              color = "Phylum",
              palette = colpalette,
              alpha = 0.75,
              size = "degree", 
              size.legend = NA,
              #edge.label = "weight", 
              #edge.size=1,
              edge.color="color",
              legend.position = "left",
              #edge.alpha = 0.5,
              label = FALSE 
              #label.size = 3,
              #edge.label.size = 3
              ) +
    guides(size = "none") +
    guides(color = guide_legend(override.aes = list(size = 2))) +
    guides(fill = guide_legend(ncol = 1)) +
    #guides(size="none", col="none") +
    ggtitle("Nafferton network")
  return(netplot)
}
  
```

Now use these functions to produce the networks and plots

```{r plot_net}
## For archaea
a_net_naff <- get_net(a_graphs[[1]], ac_naf, arch_colors_naff)
a_naff_plot <- get_netplot(a_graphs[[1]], a_net_naff[[1]], a_net_naff[[2]], y)
a_net_ous <- get_net(a_graphs[[2]], ac_ous, arch_colors_ous)
a_ous_plot <- get_netplot(a_graphs[[2]], a_net_ous[[1]], a_net_ous[[2]], y)

## For bacteria
b_net_naff <- get_net(b_graphs[[1]], bc_naf, bact_colors_naff)
b_naff_plot <- get_netplot(b_graphs[[1]], b_net_naff[[1]], b_net_naff[[2]])
b_net_ous <- get_net(b_graphs[[2]], bc_ous, bact_colors_ous)
b_ous_plot <- get_netplot(b_graphs[[2]], b_net_ous[[1]], b_net_ous[[2]])

## For eukaryotes
e_net_naff <- get_net(f_graphs[[1]], fc_naf, euk_colors_naff)
e_naff_plot <- get_netplot(f_graphs[[1]], e_net_naff[[1]], e_net_naff[[2]], y)
e_net_ous <- get_net(f_graphs[[2]], fc_ous, euk_colors_ous)
e_ous_plot <- get_netplot(f_graphs[[2]], e_net_ous[[1]], e_net_ous[[2]], y)

## For viruses
v_net_naff <- get_net(v_graphs[[1]], vc_naf, vir_colors_naff)
v_naff_plot <- get_netplot(v_graphs[[1]], v_net_naff[[1]], v_net_naff[[2]])
v_net_ous <- get_net(v_graphs[[2]], vc_ous, vir_colors_ous)
v_ous_plot <- get_netplot(v_graphs[[2]], v_net_ous[[1]], v_net_ous[[2]])
```

```{r}
#Plot farms by kingdom together
a_plot <- ggarrange(a_naff_plot, a_ous_plot, ncol = 2, nrow = 1)
b_plot <- ggarrange(b_naff_plot, b_ous_plot, ncol = 2, nrow = 1)
e_plot <- ggarrange(e_naff_plot, e_ous_plot, ncol = 2, nrow = 1)
v_plot <- ggarrange(v_naff_plot, v_ous_plot, ncol = 2, nrow = 1)
```

####COMBINATION OF NETWORKS BY KINGDOM####

First, create the functions to use multikindom SPIEC-EASI networks

```{r}
# Function to calculate the network correlations and the graph using both SPIEC-EASI and igraph for multi kingdom networks
net_fun_multi <- function(phylo, phylo_two) {
  net <- multi.spiec.easi(list(phylo, phylo_two), method="mb", lambda.min.ratio=1e-2, nlambda=20, pulsar.params=list(rep.num=100))
  pl.net <- adj2igraph(getRefit(net), vertex.attr=list(name=c(taxa_names(phylo), taxa_names(phylo_two))))
  plist <- list(net, pl.net)
  return(plist)
}
```

```{r}
## Apply network function to combination inside two lists

resultsbarch <- mapply(net_fun_multi, bcore_list, acore_list)
resultsbaek <-  mapply(net_fun_multi, bcore_list, fcore_list)
resultseukar <-  mapply(net_fun_multi, fcore_list, acore_list)
resultsbavir <- mapply(net_fun_multi, bcore_list, vcore_list)
resultsarvir <- mapply(net_fun_multi, acore_list, vcore_list)
resultseukvir <- mapply(net_fun_multi, fcore_list, vcore_list)

```

Create the necessary objects to plot by combination and farm

```{r graph_list_multi}
# Create a new function to extract the graphs from the objects created

# Function to extract the only graphs from each farm. Returns a list that can be fed to the next function
grap_list_multi <- function(netlist){
  finalist <-  list()
  finalist[1] <- netlist[2,1]
  finalist[2] <- netlist[2,2]
  return(finalist)
}

```


```{r}
#Get the graphs and metrics

baek_graphs <- grap_list_multi(resultsbaek) # List of graphs for each farm
baek_metrics <- lapply(baek_graphs, net_met) # List of metrics for each graph

barch_graphs <- grap_list_multi(resultsbarch)
barch_metrics <- lapply(barch_graphs, net_met)

eukar_graphs <- grap_list_multi(resultseukar)
eukar_metrics <- lapply(eukar_graphs, net_met)

bavir_graphs <- grap_list_multi(resultsbavir)
bavir_metrics <- lapply(bavir_graphs, net_met)

arvir_graphs <- grap_list_multi(resultsarvir)
arvir_metrics <- lapply(arvir_graphs, net_met)

eukvir_graphs <- grap_list_multi(resultseukvir)
eukvir_metrics <- lapply(eukvir_graphs, net_met)

# Finalize network plots

baek_naff <- resultsbaek[,1]
baek_ous <- resultsbaek[,2]
baek_colors_naff <- do.call(color_edges, baek_naff)
baek_colors_ous <- do.call(color_edges, baek_ous)

barch_naff <- resultsbarch[,1]
barch_ous <- resultsbarch[,2]
barch_colors_naff <- do.call(color_edges, barch_naff)
barch_colors_ous <- do.call(color_edges, barch_ous)

eukar_naff <- resultseukar[,1]
eukar_ous <- resultseukar[,2]
eukar_colors_naff <- do.call(color_edges, eukar_naff)
eukar_colors_ous <- do.call(color_edges, eukar_ous)

bavir_naff <- resultsbavir[,1]
bavir_ous <- resultsbavir[,2]
bavir_colors_naff <- do.call(color_edges, bavir_naff)
bavir_colors_ous <- do.call(color_edges, bavir_ous)

arvir_naff <- resultsarvir[,1]
arvir_ous <- resultsarvir[,2]
arvir_colors_naff <- do.call(color_edges, arvir_naff)
arvir_colors_ous <- do.call(color_edges, arvir_ous)

eukvir_naff <- resultseukvir[,1]
eukvir_ous <- resultseukvir[,2]
eukvir_colors_naff <- do.call(color_edges, eukvir_naff)
eukvir_colors_ous <- do.call(color_edges, eukvir_ous)
```

Create the functions adapted to extract the node info from two different phyloseq objects

```{r get_net}
## Function to produce network plot
colnames(v_naff_phy@tax_table) <- c("Kingdom", "Phylum", "Class", "Order", "Family", "Genus", "Species")
colnames(v_ous_phy@tax_table) <- c("Kingdom", "Phylum", "Class", "Order", "Family", "Genus", "Species")

get_net_multi <- function(qgraph, physeq, physeq2, colres){
  # Associate colors to graph
  E(qgraph)$color=colres[[3]]
  E(qgraph)$weight=colres[[4]]
  # Pick node name to the Genus level
  tax_table(physeq) <- tax_table(physeq)[,"Phylum"]
  tax_table(physeq2) <- tax_table(physeq2)[,'Kingdom']
  #Taxa names for microbes in pseq 1 and 2
  otu_ids <- V(qgraph)$name
  idx <- which(row.names(tax_table(physeq)) %in% otu_ids)
  taxa <- as.character(tax_table(physeq)[,"Phylum"])[idx]
  votu_ids <- V(qgraph)$name
  vidx <- which(row.names(tax_table(physeq2)) %in% votu_ids)
  vtaxa <- as.character(tax_table(physeq2)[,"Kingdom"])[vidx]
  #Network adaptations
  net <- asNetwork(qgraph)
  network.vertex.names(net) <- c(taxa, vtaxa)
  net %v% "Kingdom" = as.character(c(taxa,vtaxa))
  return(list(net, taxa, vtaxa))
}

nb_nodes <- vcount(eukvir_ous_topnet)
y= col_vector74[1:nb_nodes]
names(y) <- levels(as.factor(c(eukvir_net_ous[[2]], eukvir_net_ous[[3]])))
get_netplot_multi <- function(qgraph, net, taxa, vtaxa, colpalette){
  #nb_nodes <- vcount(qgraph)
  #y= col_vector74[1:nb_nodes]
  #names(y) <- levels(as.factor(c(taxa, vtaxa)))
  netplot <- ggnet2(net,
              color = "Kingdom",
              palette = colpalette,
              alpha = 0.75,
              #size = 6,
              size = "degree",
              size.legend = NA,
              #edge.label = "weight", 
              #edge.size=1,
              edge.color="color",
              legend.position = "left",
              #edge.alpha = 0.5,
              label = FALSE
              #label.size = 3,
              #edge.label.size = 3
              ) +
    guides(size='none') +
    guides(color = guide_legend(override.aes = list(size = 3))) +
    #guides(col="none") +
    ggtitle("Nafferton network")
  return(netplot)
}
```

Produce the final plots for each network

```{r plots, results='hide'}
## For bac+euk
baek_net_naff <- get_net_multi(baek_graphs[[1]], bc_naf, fc_naf, baek_colors_naff)
baek_naff_plot <- get_netplot_multi(baek_graphs[[1]], baek_net_naff[[1]], baek_net_naff[[2]], baek_net_naff[[3]])
baek_net_ous <- get_net_multi(baek_graphs[[2]], bc_ous, fc_ous, baek_colors_ous)
baek_ous_plot <- get_netplot_multi(baek_graphs[[2]], baek_net_ous[[1]], baek_net_ous[[2]], baek_net_ous[[3]])

## For bac+arch
barch_net_naff <- get_net_multi(barch_graphs[[1]], bc_naf, ac_naf, barch_colors_naff)
barch_naff_plot <- get_netplot_multi(barch_graphs[[1]], barch_net_naff[[1]], barch_net_naff[[2]], barch_net_naff[[3]])
barch_net_ous <- get_net_multi(barch_graphs[[2]], bc_ous, ac_ous, barch_colors_ous)
barch_ous_plot <- get_netplot_multi(barch_graphs[[2]], barch_net_ous[[1]], barch_net_ous[[2]], barch_net_ous[[3]])

## For arch+euk
eukar_net_naff <- get_net_multi(eukar_graphs[[1]], ac_naf, fc_naf, eukar_colors_naff)
eukar_naff_plot <- get_netplot_multi(eukar_graphs[[1]], eukar_net_naff[[1]], eukar_net_naff[[2]], eukar_net_naff[[3]])
eukar_net_ous <- get_net_multi(eukar_graphs[[2]], ac_ous, fc_ous, eukar_colors_ous)
eukar_ous_plot <- get_netplot_multi(eukar_graphs[[2]], eukar_net_ous[[1]], eukar_net_ous[[2]], eukar_net_ous[[3]])

## For bac+vir
bavir_net_naff <- get_net_multi(bavir_graphs[[1]], bc_naf, v_naff_phy, bavir_colors_naff)
bavir_naff_plot <- get_netplot_multi(bavir_graphs[[1]], bavir_net_naff[[1]], bavir_net_naff[[2]], bavir_net_naff[[3]])
bavir_net_ous <- get_net_multi(bavir_graphs[[2]], bc_ous, v_ous_phy, bavir_colors_ous)
bavir_ous_plot <- get_netplot_multi(bavir_graphs[[2]], bavir_net_ous[[1]], bavir_net_ous[[2]], bavir_net_ous[[3]])

## For vir+arch
arvir_net_naff <- get_net_multi(arvir_graphs[[1]], ac_naf, v_naff_phy, arvir_colors_naff)
arvir_naff_plot <- get_netplot_multi(arvir_graphs[[1]], arvir_net_naff[[1]], arvir_net_naff[[2]], arvir_net_naff[[3]])
arvir_net_ous <- get_net_multi(arvir_graphs[[2]], ac_ous, v_ous_phy, arvir_colors_ous)
arvir_ous_plot <- get_netplot_multi(arvir_graphs[[2]], arvir_net_ous[[1]], arvir_net_ous[[2]], arvir_net_ous[[3]])

## For vir+euk
eukvir_net_naff <- get_net_multi(eukvir_graphs[[1]], fc_naf, v_naff_phy, eukvir_colors_naff)
eukvir_naff_plot <- get_netplot_multi(eukvir_graphs[[1]], eukvir_net_naff[[1]], eukvir_net_naff[[2]], eukvir_net_naff[[3]])
eukvir_net_ous <- get_net_multi(eukvir_graphs[[2]], fc_ous, v_ous_phy, eukvir_colors_ous)
eukvir_ous_plot <- get_netplot_multi(eukvir_graphs[[2]], eukvir_net_ous[[1]], eukvir_net_ous[[2]], eukvir_net_ous[[3]])
```

Create phyloseq object with top 25 OTU by kingdom for easy plots

```{r top_otu, results='hide'}
top_otu <- function(phylo){
  top.names <- names(sort(taxa_sums(phylo), TRUE)[1:25])
  top <- prune_taxa(top.names, phylo)
  top.pseq <- prune_taxa(taxa_names(top), phylo)
  return(top.pseq)
}

#Calculate top 25 OTUs per farm and kingdom
top_bac_naf <- top_otu(bc_naf)
top_bac_ous <- top_otu(bc_ous)
top_arc_naf <- top_otu(ac_naf)
top_arc_ous <- top_otu(ac_ous)
top_euk_naf <- top_otu(fc_naf)
top_euk_ous <- top_otu(fc_ous)
top_vir_naf <- top_otu(v_naff_phy)
top_vir_ous <- top_otu(v_ous_phy)
```

```{r top_graph}
# Function to extract the subgraph with 25 OTU
top_graph <- function(phylo, phylo2, qgraph){
  nodes_of_interest <- c(taxa_names(phylo), taxa_names(phylo2))
  selnodes <- V(qgraph)[name %in% nodes_of_interest]
  selegoV <- ego(qgraph, order=1, nodes = selnodes, mode = "all", mindist = 0)
  top.graph <- induced_subgraph(qgraph,unlist(selegoV))
  return(top.graph)
}

top_graph_single <- function(phylo, qgraph){
  nodes_of_interest <- taxa_names(phylo)
  selnodes <- V(qgraph)[name %in% nodes_of_interest]
  selegoV <- ego(qgraph, order=1, nodes = selnodes, mode = "all", mindist = 0)
  top.graph <- induced_subgraph(qgraph,unlist(selegoV))
  return(top.graph)
}
```

```{r}
baek_naff_topnet <- top_graph(top_bac_naf, top_euk_naf, baek_graphs[[1]])
baek_ous_topnet <- top_graph(top_bac_ous, top_euk_ous, baek_graphs[[2]])
barch_naff_topnet <- top_graph(top_bac_naf, top_arc_naf, barch_graphs[[1]])
barch_ous_topnet <- top_graph(top_bac_ous, top_arc_ous, barch_graphs[[2]])
eukar_naff_topnet <- top_graph(top_arc_naf, top_euk_naf, eukar_graphs[[1]])
eukar_ous_topnet <- top_graph(top_arc_ous, top_euk_ous, eukar_graphs[[2]])
bavir_naff_topnet <- top_graph(top_bac_naf, top_vir_naf, bavir_graphs[[1]])
bavir_ous_topnet <- top_graph(top_bac_ous, top_vir_ous, bavir_graphs[[2]])
arvir_naff_topnet <- top_graph(top_arc_naf, top_vir_naf, arvir_graphs[[1]])
arvir_ous_topnet <- top_graph(top_arc_ous, top_vir_ous, arvir_graphs[[2]])
eukvir_naff_topnet <- top_graph(top_euk_naf, top_vir_naf, eukvir_graphs[[1]])
eukvir_ous_topnet <- top_graph(top_euk_ous, top_vir_ous, eukvir_graphs[[2]])

```

Obtain top networks from single-kingdom plots

```{r}
b_naff_topnet <- top_graph_single(top_bac_naf, b_graphs[[1]])
b_ous_topnet <- top_graph_single(top_bac_ous, b_graphs[[2]])
a_naff_topnet <- top_graph_single(top_arc_naf, a_graphs[[1]])
a_ous_topnet <- top_graph_single(top_arc_ous, a_graphs[[2]])
f_naff_topnet <- top_graph_single(top_euk_naf, f_graphs[[1]])
f_ous_topnet <- top_graph_single(top_euk_ous, f_graphs[[2]])
v_naff_topnet <- top_graph_single(top_vir_naf, v_graphs[[1]])
v_ous_topnet <- top_graph_single(top_vir_ous, v_graphs[[2]])
```



Produce new plots with the top 25 OTUs. First, for the single-kingdom plots:

```{r results='hide'}
## For archaea
arch_colors_naff <- color_edges(a_naff[[1]], a_naff_topnet)
a_net_naff <- get_net(a_naff_topnet, ac_naf, arch_colors_naff)
a_naff_plot <- get_netplot(a_naff_topnet, a_net_naff[[1]], a_net_naff[[2]], y)
arch_colors_ous <- color_edges(a_ous[[1]], a_ous_topnet)
a_net_ous <- get_net(a_ous_topnet, ac_ous, arch_colors_ous)
a_ous_plot <- get_netplot(a_graphs[[2]], a_net_ous[[1]], a_net_ous[[2]], y)

## For bacteria
bact_colors_naff <- color_edges(b_naff[[1]], b_naff_topnet)
b_net_naff <- get_net(b_naff_topnet, bc_naf, bact_colors_naff)
b_naff_plot <- get_netplot(b_naff_topnet, b_net_naff[[1]], b_net_naff[[2]], y)
bact_colors_ous <- color_edges(b_ous[[1]], b_ous_topnet)
b_net_ous <- get_net(b_ous_topnet, bc_ous, bact_colors_ous)
b_ous_plot <- get_netplot(b_ous_topnet, b_net_ous[[1]], b_net_ous[[2]], y)

## For eukaryotes
euk_colors_naff <- color_edges(f_naff[[1]], f_naff_topnet)
e_net_naff <- get_net(f_naff_topnet, fc_naf, euk_colors_naff)
e_naff_plot <- get_netplot(f_naff_topnet, e_net_naff[[1]], e_net_naff[[2]], y)
euk_colors_ous <- color_edges(f_ous[[1]], f_ous_topnet)
e_net_ous <- get_net(f_ous_topnet, fc_ous, euk_colors_ous)
e_ous_plot <- get_netplot(f_ous_topnet, e_net_ous[[1]], e_net_ous[[2]], y)

## For viruses
vir_colors_naff <- color_edges(v_naff[[1]], v_naff_topnet)
v_net_naff <- get_net(v_naff_topnet, vc_naf, vir_colors_naff)
v_naff_plot <- get_netplot(v_naff_topnet, v_net_naff[[1]], v_net_naff[[2]])
vir_colors_ous <- color_edges(v_ous[[1]], v_ous_topnet)
v_net_ous <- get_net(v_ous_topnet, vc_ous, vir_colors_ous)
v_ous_plot <- get_netplot(v_ous_topnet, v_net_ous[[1]], v_net_ous[[2]])
```


```{r new_plot, echo=TRUE, results='hide'}
## For bac+euk
baek_colors_naff <- color_edges(baek_naff[[1]], baek_naff_topnet)
baek_net_naff <- get_net_multi(baek_naff_topnet, bc_naf, fc_naf, baek_colors_naff)
baek_naff_plot <- get_netplot_multi(baek_naff_topnet, baek_net_naff[[1]], baek_net_naff[[2]], baek_net_naff[[3]])
#Ouseburn
baek_colors_ous <- color_edges(baek_ous[[1]], baek_ous_topnet)
baek_net_ous <- get_net_multi(baek_ous_topnet, bc_ous, fc_ous, baek_colors_ous)
baek_ous_plot <- get_netplot_multi(baek_ous_topnet, baek_net_ous[[1]], baek_net_ous[[2]], baek_net_ous[[3]])

## For bac+arch
barch_colors_naff <- color_edges(barch_naff[[1]], barch_naff_topnet)
barch_net_naff <- get_net_multi(barch_naff_topnet, bc_naf, ac_naf, barch_colors_naff)
barch_naff_plot <- get_netplot_multi(barch_naff_topnet, barch_net_naff[[1]], barch_net_naff[[2]], barch_net_naff[[3]])
#Ouseburn
barch_colors_ous <- color_edges(barch_ous[[1]], barch_ous_topnet)
barch_net_ous <- get_net_multi(barch_ous_topnet, bc_ous, ac_ous, barch_colors_ous)
barch_ous_plot <- get_netplot_multi(barch_ous_topnet, barch_net_ous[[1]], barch_net_ous[[2]], barch_net_ous[[3]])

## For arch+euk
eukar_colors_naff <- color_edges(eukar_naff[[1]], eukar_naff_topnet)
eukar_net_naff <- get_net_multi(eukar_naff_topnet, ac_naf, fc_naf, eukar_colors_naff)
eukar_naff_plot <- get_netplot_multi(eukar_naff_topnet, eukar_net_naff[[1]], eukar_net_naff[[2]], eukar_net_naff[[3]])
#Ouseburn
eukar_colors_ous <- color_edges(eukar_ous[[1]], eukar_ous_topnet)
eukar_net_ous <- get_net_multi(eukar_ous_topnet, ac_ous, fc_ous, eukar_colors_ous)
eukar_ous_plot <- get_netplot_multi(eukar_ous_topnet, eukar_net_ous[[1]], eukar_net_ous[[2]], eukar_net_ous[[3]])

## For bac+vir
bavir_colors_naff <- color_edges(bavir_naff[[1]], bavir_naff_topnet)
bavir_net_naff <- get_net_multi(bavir_naff_topnet, bc_naf, v_naff_phy, bavir_colors_naff)
bavir_naff_plot <- get_netplot_multi(bavir_naff_topnet, bavir_net_naff[[1]], bavir_net_naff[[2]], bavir_net_naff[[3]])
#Ouseburn
bavir_colors_ous <- color_edges(bavir_ous[[1]], bavir_ous_topnet)
bavir_net_ous <- get_net_multi(bavir_ous_topnet, bc_ous, v_ous_phy, bavir_colors_ous)
bavir_ous_plot <- get_netplot_multi(bavir_ous_topnet, bavir_net_ous[[1]], bavir_net_ous[[2]], bavir_net_ous[[3]])

## For vir+arch
arvir_colors_naff <- color_edges(arvir_naff[[1]], arvir_naff_topnet)
arvir_net_naff <- get_net_multi(arvir_naff_topnet, ac_naf, v_naff_phy, arvir_colors_naff)
arvir_naff_plot <- get_netplot_multi(arvir_naff_topnet, arvir_net_naff[[1]], arvir_net_naff[[2]], arvir_net_naff[[3]], y)
#Ouseburn
arvir_colors_ous <- color_edges(arvir_ous[[1]], arvir_ous_topnet)
arvir_net_ous <- get_net_multi(arvir_ous_topnet, ac_ous, v_ous_phy, arvir_colors_ous)
arvir_ous_plot <- get_netplot_multi(arvir_ous_topnet, arvir_net_ous[[1]], arvir_net_ous[[2]], arvir_net_ous[[3]], y)

## For vir+euk
eukvir_colors_naff <- color_edges(eukvir_naff[[1]], eukvir_naff_topnet)
eukvir_net_naff <- get_net_multi(eukvir_naff_topnet, fc_naf, v_naff_phy, eukvir_colors_naff)
eukvir_naff_plot <- get_netplot_multi(eukvir_naff_topnet, eukvir_net_naff[[1]], eukvir_net_naff[[2]], eukvir_net_naff[[3]], y)
#Ouseburn
eukvir_colors_ous <- color_edges(eukvir_ous[[1]], eukvir_ous_topnet)
eukvir_net_ous <- get_net_multi(eukvir_ous_topnet, fc_ous, v_ous_phy, eukvir_colors_ous)
eukvir_ous_plot <- get_netplot_multi(eukvir_ous_topnet, eukvir_net_ous[[1]], eukvir_net_ous[[2]], eukvir_net_ous[[3]], y)
```

Now, structure the all the network plots

```{r}
baek_plot <- ggarrange(baek_naff_plot, baek_ous_plot, ncol = 2, nrow = 1)
barch_plot <- ggarrange(barch_naff_plot, barch_ous_plot, ncol = 2, nrow = 1)
eukar_plot <- ggarrange(eukar_naff_plot, eukar_ous_plot, ncol = 2, nrow = 1)
bavir_plot <- ggarrange(bavir_naff_plot, bavir_ous_plot, ncol = 2, nrow = 1)
arvir_plot <- ggarrange(arvir_naff_plot, arvir_ous_plot, ncol = 2, nrow = 1)
eukvir_plot <- ggarrange(eukvir_naff_plot, eukvir_ous_plot, ncol = 2, nrow = 1)
blank <- plot.new()

net_final_plot <- grid.arrange(b_plot, baek_plot, barch_plot, bavir_plot, e_plot, eukar_plot, eukvir_plot, a_plot, arvir_plot, v_plot, blank, ncol = 4, layout_matrix = cbind(c(1,2,3,4), c(11,5,6,7), c(11,11,8,9), c(11,11,11,10)))

ggsave(file="final_net_plot_4.svg", plot=net_final_plot, width=45, height=20)
```

Separate the final plots into chunks for better visualization on the thesis document

```{r}
top_plot <- grid.arrange(b_plot, baek_plot, barch_plot, bavir_plot, e_plot, eukar_plot, eukvir_plot, blank, layout_matrix = cbind(c(1,2, 3, 4), c(8, 5, 6, 7)))
ggsave(file="top_net_plot.svg", plot=top_plot, width=18, height=15)
bottom_plot <- grid.arrange(a_plot, arvir_plot, v_plot, blank, layout_matrix = cbind(c(1,2), c(4, 3)))
ggsave(file="bottom_net_plot.svg", plot=bottom_plot, width=20, height=8)
```



