---
title: "Environmental analysis based on sample location"
author: "Bea"
date: "2023-08-11"
output: html_document
---

```{r setup, include=FALSE}
library("phyloseq")
library("ggplot2")
library("RColorBrewer")
library("patchwork")
library("microbiome")
library("ape")
library("vegan")
library("tidyverse")
library("viridis")
library("grid")
library("readxl")
library("eulerr")
library("microbiomeutilities")
library("wesanderson")
library("ggsci")
library("ggvenn")

knitr::opts_chunk$set(echo = TRUE)
```

## STEP 1. Subset the phyloseq object

We're subsetting the phyloseq object to retain only samples coming from the offices and animal dwellings

```{r subset}

sub_pseq <- subset_samples(scr_pseq, RoomType == "Off" | RoomType == "AD") 
sub_df <- prune_taxa(taxa_sums(sub_pseq) > 10000, sub_pseq) %>% 
  tax_glom(taxrank = "Phylum") %>% 
  #transform_sample_counts(function(x) {x/sum(x)}) %>%
  psmelt() %>% 
  arrange(Phylum)
```

Now create the plots using geom_area

```{r plot}
off_plot <- sub_df %>% 
  mutate(Time = as_date(Time)) %>% 
  mutate(Room_position = replace_na(Room_position, "Single")) %>% 
  #filter(Room == "OfficeNaff") %>% 
  group_by(Room, Room_position, Time, Phylum) %>%
  summarise(n = sum(Abundance)) %>% 
  mutate(percentage = n / sum(n)) %>% 
  ggplot(aes(x= Time, y = percentage, fill = Phylum)) +
  #geom_bar(stat = "identity") +
  geom_area(alpha=0.6, size=.5, colour="white", position = "stack") +
  scale_fill_viridis(discrete = TRUE, option = "mako") +
  #scale_x_discrete(guide = guide_axis(angle = 45)) +
  #facet_grip(~Room_position, scales = "free_x", space = "free_x") +
  facet_wrap(Room ~ Room_position, strip.position = "top", scales = "free") +
  scale_x_date(labels = c("Summer", "Winter", "Spring")) +
  theme(strip.text.x = element_text(size=10)) +
  guides(fill=guide_legend(title = "Taxa", ncol = 3)) +
  ggtitle("Microbial diversity changes by room location")

```

Now onto another graph. We need to plot the average humidity and temperatures at each farm. That info is stored in two different sheets in the same excel file

```{r weather}

weather_ous <- read_xlsx("./weather_history.xlsx", sheet = "Newcastle", col_names = TRUE) %>% 
  mutate(Date = as.Date(Var, format = "%Y/%m/%d")) %>% 
  select(-Var)
weather_naf <- read_xlsx("./weather_history.xlsx", sheet = "Stocksfield", col_names = TRUE) %>% 
  mutate(Date = as.Date(Var, format = "%Y/%m/%d")) %>% 
  select(-Var)

```


Plot with combined temperature (as line) and humidity (as bars).

```{r loc_plot}
naf_plot1 <- ggplot(weather_naf, aes(Date)) +
  geom_ribbon(aes(ymin = `Low Temp`, ymax= `High Temp`), fill = "lightcyan2") +
  geom_line(aes(y = `Av. Temp`), colour = "lightseagreen") +
  geom_line(aes(y = `High Temp`), colour = "red") +
  geom_line(aes(y = `Low Temp`), colour = "blue") + 
  scale_x_date(date_breaks = "1 month",  date_labels = "%m/%Y") +
  theme_minimal() +
  theme(axis.title.x = element_blank(), axis.text.x = element_blank())

naf_plot2 <- ggplot(weather_naf, aes(Date)) +
  geom_bar(aes(y = `Av. Hum`), fill = "lightskyblue1", stat = "identity") +
  geom_line(aes(y = `High Hum`), colour = "mediumorchid3") +
  geom_line(aes(y = `Low Hum`), colour = "mediumturquoise") + 
  scale_x_date(date_breaks = "1 month", date_labels = "%m/%Y") +
  theme_minimal() +
  theme(axis.title.x = element_blank(),axis.text.x = element_text(angle=45))

```

```{r plot_naf}
grid.newpage()
grid.draw(rbind(ggplotGrob(naf_plot1), ggplotGrob(naf_plot2), size = "last"))
```

### VENN DIAGRAMS PER TYPE OF ROOM AND FARM ###

To compare the microbial features shared by the different offices and animal dwellings, let's create a Venn diagram.

```{r}
table(meta(sub_pseq)$Room, useNA = "always")
sub.pseqrel <- microbiome::transform(sub_pseq, "compositional")
room_list <- unique(as.character(meta(sub.pseqrel)$Room))
```
```{r}
## Find the core microorganisms in each room, independently of location inside room and time of colection

list_core <- c()

for (n in room_list) {
  ps.sub <-  subset_samples(sub.pseqrel, Room == n)
  core_m <- core_members(ps.sub,
                         detection = 0.001,
                         prevalence = 0.90) # 1 % in at least 90% samples
  print(paste0("No. of core taxa in ", n, " : ", length(core_m)))
  list_core[[n]] <- core_m
}
```
```{r}
print(list_core)
```
```{r}
#Specify colours for the venn diagram

mycols <- c(Cafe = "lightblue", OfficeOus = "lightcoral", OfficeNaff = "lightgoldenrod", CafeEntrance = "seashell2")
plot(venn(list_core[c("OfficeOus", "OfficeNaff", "Cafe", "CafeEntrance")]),
     fills = mycols)

ggvenn(list_core[c("OfficeOus", "OfficeNaff", "Cafe", "CafeEntrance")], fill_color = c("lightblue", "lightcoral", "lightgoldenrod",  "seashell2"), stroke_size = 0, set_name_size = 7, show_percentage = FALSE, text_size = 7)
```

```{r}
mycols <- c(PigDwell = "lightpink", CowShed = "lightseagreen", MilkingBld = "darkseagreen", CalfShed = "deeppink3")
plot(venn(list_core[c("PigDwell", "CowShed", "CalfShed", "MilkingBld")]), fills = mycols)

ggvenn(list_core[c("PigDwell", "CowShed", "CalfShed", "MilkingBld")], fill_color = c("lightpink", "lightseagreen", "darkseagreen",  "deeppink3"), stroke_size = 0, set_name_size = 7, show_percentage = FALSE, text_size = 7)
```
Find the common microorganisms between samples in different locations of the same room

```{r}
otufun <- function(room, dis) {
  listy <-  list()
  #r <-  substitute(room)
  #p <-  substitute(dis)
  ps.sub <- subset_samples(sub.pseqrel, Room == room & Room_position == dis)
  #core_m <- core_members(ps.sub, detection = 0.001, prevalence = 0.90)
  #print(paste0("No. of core taxa in ", r, " : ", length(core_m)))
  #listy[[substitute(dis)]] <- core_m
  #return(listy)
  ps.sub
}
```

```{r}
Cafe_list <- list()
Cafe_list$Right <- subset_samples(sub.pseqrel, Room == "Cafe" & Room_position == "Right") %>% 
  core_members(detection = 0.001, prevalence = 0.9)
Cafe_list$Left <- subset_samples(sub.pseqrel, Room == "Cafe" & Room_position == "Left") %>% 
  core_members(detection = 0.001, prevalence = 0.9)
Cafe_list$Middle <- subset_samples(sub.pseqrel, Room == "Cafe" & Room_position == "Middle") %>% 
  core_members(detection = 0.001, prevalence = 0.9)
OfficeOus <- list()
OfficeOus$Right <- subset_samples(sub.pseqrel, Room == "OfficeOus" & Room_position == "Right") %>% 
  core_members(detection = 0.001, prevalence = 0.9)
OfficeOus$Left <- subset_samples(sub.pseqrel, Room == "OfficeOus" & Room_position == "Left") %>% 
  core_members(detection = 0.001, prevalence = 0.9)
OfficeNaff <- list()
OfficeNaff$Right <- subset_samples(sub.pseqrel, Room == "OfficeNaff" & Room_position == "Right") %>% 
  core_members(detection = 0.001, prevalence = 0.9)
OfficeNaff$Left <- subset_samples(sub.pseqrel, Room == "OfficeNaff" & Room_position == "Left") %>% 
  core_members(detection = 0.001, prevalence = 0.9)
```

```{r}
ggvenn(Cafe_list, fill_color = c("#009E73", "#E69F00", "#56B4E9"), stroke_size = 0, set_name_size = 7, show_percentage = FALSE) +
  ggtitle("Venn diagram of samples from Cafe at Ouseburn")
```
```{r}
ggvenn(OfficeNaff, fill_color = c("#009E73", "#E69F00"), stroke_size = 0, set_name_size = 7, show_percentage = FALSE, text_size = 8) +
  ggtitle("Venn diagram of samples from Office at Nafferton")
```
```{r}
ggvenn(OfficeOus, fill_color = c("hotpink2", "paleturquoise"), stroke_size = 0, set_name_size = 7, show_percentage = FALSE, text_size = 8) +
  ggtitle("Venn diagram of samples from Office at Ouseburn") 
```
Find the Venn diagram intersection and match the OTU names to their taxonomy in the dataset

```{r intersec}
## Get the list of OTUs in the intersection
inter_offs <- as.list(Reduce(intersect, list_core[c("OfficeOus", "OfficeNaff", "Cafe", "CafeEntrance")]))
inter_anim <- as.list(Reduce(intersect, list_core[c("PigDwell", "CowShed", "CalfShed", "MilkingBld")]))
inter_offnaf <- as.list(Reduce(intersect, OfficeNaff))
inter_offous <- as.list(Reduce(intersect, OfficeOus))
inter_caf <- as.list(Reduce(intersect, Cafe_list))
```

```{r get_taxa_df}
df_offs <-  subset_taxa(scr_pseq, rownames(otu_table(scr_pseq)) %in% inter_offs) %>% 
    tax_table() %>% 
    as.data.frame()

df_anim <-  subset_taxa(scr_pseq, rownames(otu_table(scr_pseq)) %in% inter_anim) %>% 
    tax_table() %>% 
    as.data.frame()

df_offnaf <-  subset_taxa(scr_pseq, rownames(otu_table(scr_pseq)) %in% inter_offnaf) %>% 
    tax_table() %>% 
    as.data.frame()

df_offous <-  subset_taxa(scr_pseq, rownames(otu_table(scr_pseq)) %in% inter_offous) %>% 
    tax_table() %>% 
    as.data.frame()

df_caf <-  subset_taxa(scr_pseq, rownames(otu_table(scr_pseq)) %in% inter_caf) %>% 
    tax_table() %>% 
    as.data.frame()
```

Find the distinctive OTUs in each room (those OTUs that are not shared)

```{r non-shared}
## Extract OTU names
a <- list_core[c("OfficeOus", "OfficeNaff", "Cafe", "CafeEntrance")]
offs_un <- lapply(1:length(a), function(n) setdiff(a[[n]], unlist(a[-n])))

b <- list_core[c("PigDwell", "CowShed", "CalfShed", "MilkingBld")]
anim_un <- lapply(1:length(b), function(n) setdiff(b[[n]], unlist(b[-n])))

## Produce dfs with the full taxonomic names

df_offnaff_un <- subset_taxa(scr_pseq, rownames(otu_table(scr_pseq)) %in% offs_un[[2]]) %>% 
    tax_table() %>% 
    as.data.frame()
df_cafe_un <- subset_taxa(scr_pseq, rownames(otu_table(scr_pseq)) %in% offs_un[[3]]) %>% 
    tax_table() %>% 
    as.data.frame()
df_calf_un <- subset_taxa(scr_pseq, rownames(otu_table(scr_pseq)) %in% anim_un[[3]]) %>% 
    tax_table() %>% 
    as.data.frame()
df_cow_un <- subset_taxa(scr_pseq, rownames(otu_table(scr_pseq)) %in% anim_un[[2]]) %>% 
    tax_table() %>% 
    as.data.frame()
df_pig_un <- subset_taxa(scr_pseq, rownames(otu_table(scr_pseq)) %in% anim_un[[1]]) %>% 
    tax_table() %>% 
    as.data.frame()
df_cafent_un <- subset_taxa(scr_pseq, rownames(otu_table(scr_pseq)) %in% offs_un[[4]]) %>% 
    tax_table() %>% 
    as.data.frame()
df_milk_un <- subset_taxa(scr_pseq, rownames(otu_table(scr_pseq)) %in% anim_un[[4]]) %>% 
    tax_table() %>% 
    as.data.frame()

```

```{r}
offnaf_un <- lapply(1:length(OfficeNaff), function(n) setdiff(OfficeNaff[[n]], unlist(OfficeNaff[-n])))
offous_un <- lapply(1:length(OfficeOus), function(n) setdiff(OfficeOus[[n]], unlist(OfficeOus[-n])))

df_offous_r <- subset_taxa(scr_pseq, rownames(otu_table(scr_pseq)) %in% offous_un[[1]]) %>% 
    tax_table() %>% 
    as.data.frame()
df_offous_l <- subset_taxa(scr_pseq, rownames(otu_table(scr_pseq)) %in% offous_un[[2]]) %>% 
    tax_table() %>% 
    as.data.frame()
df_offnaf_r <- subset_taxa(scr_pseq, rownames(otu_table(scr_pseq)) %in% offnaf_un[[1]]) %>% 
    tax_table() %>% 
    as.data.frame()
df_offnaf_l <- subset_taxa(scr_pseq, rownames(otu_table(scr_pseq)) %in% offnaf_un[[2]]) %>% 
    tax_table() %>% 
    as.data.frame()
```

